---
title: "Cleanup Vegetation Data"
format: html
editor_options: 
  chunk_output_type: console
---

## Description

Certain misidentification problems:
Acinos arvensis vs alpinus
Up to July: different Epipactis species
Calamagrostis varia vs. Brachypodium rupestre vs. Brachypodium sylvaticum

```{r}
library(readr)
library(stringr)
library(dplyr)


beobachtungen <- read_delim("../Daten/Leuk/Climax Daten 2024/Orig_InfoFlora_Beobachtungen.csv")
length(unique(beobachtungen$releve_id))
length(beobachtungen$releve_id)

header <- read_delim("../Daten/Leuk/Climax Daten 2024/Orig_Header-Vegetations-Aufnahmen.csv")
header$name <- as.numeric(header$name)

assertthat::are_equal(61, length(unique(beobachtungen$releve_id)))

replace_species_on_plot <- function(orig_name, new_name, plot_id, ignore_cf) {
  data_with_global_plot_ids <- inner_join(header, beobachtungen, by = join_by(id == releve_id))
  info_flora_id <- data_with_global_plot_ids$id[data_with_global_plot_ids$taxon_orig == orig_name & data_with_global_plot_ids$name == plot_id]
  if(ignore_cf) {
    info_flora_id <- data_with_global_plot_ids$id[str_replace_all(data_with_global_plot_ids$taxon_orig, "cf\\. ", "") == orig_name & data_with_global_plot_ids$name == plot_id]
  }
  if(is.na(info_flora_id)) {
    message(paste("Could not find ", orig_name, " on plot ", plot_id, sep = ""))
  }
  
  if(ignore_cf) {
    beobachtungen$taxon_orig[str_replace_all(beobachtungen$taxon_orig, "cf\\. ", "") == orig_name & beobachtungen$releve_id == info_flora_id] <- new_name
  } else {
    beobachtungen$taxon_orig[beobachtungen$taxon_orig == orig_name & beobachtungen$releve_id == info_flora_id] <- new_name
  }
  beobachtungen
}

replace_species <- function(orig_name, new_name, ignore_cf) {
  if(ignore_cf) {
    beobachtungen$taxon_orig[str_replace_all(beobachtungen$taxon_orig, "cf\\. ", "") == orig_name] <- new_name
  } else {
    beobachtungen$taxon_orig[beobachtungen$taxon_orig == orig_name] <- new_name
  }
  beobachtungen
}

plot_numbers_of_species <- function(species_list) {
  species_list <- unique(species_list)
  data_with_global_plot_ids <- inner_join(header, beobachtungen, by = join_by(id == releve_id))

  plots_containing_species <- 
    data_with_global_plot_ids[data_with_global_plot_ids$taxon_orig %in% species_list,c("name", "taxon_orig")]
  plots_containing_species[order(plots_containing_species$taxon_orig),]
}

global_id_to_releve_id <- function(global_id) {
  data_with_global_plot_ids <- inner_join(header, beobachtungen, by = join_by(id == releve_id))
  data_with_global_plot_ids$id[data_with_global_plot_ids$name == global_id][1]
}

add_species_to_plot <- function(taxon, global_id) {
  releve_id <- global_id_to_releve_id(global_id)
  subset <- beobachtungen[beobachtungen$releve_id == releve_id,]
  row <- subset[1,]
  row$taxon_orig <- taxon
  row$cover <- 0.01
  beobachtungen <- rbind(beobachtungen, row)
  beobachtungen
}

# Fix naming of sp. to spec.
beobachtungen$taxon_orig <- str_replace_all(beobachtungen$taxon_orig, " sp\\.", " spec.")

# Re-identified at home or by memory...
beobachtungen <- replace_species_on_plot("Carex frigida", "Luzula spicata", 191, T)
beobachtungen <- replace_species_on_plot("Phleum phleoides", "Phleum hirsutum", 285, T)
beobachtungen <- replace_species_on_plot("Bufonia paniculata", "Minuartia spec.", 769, T)
beobachtungen <- replace_species_on_plot("Orlaya grandiflora", "Apiaceae", 702, T)
beobachtungen <- replace_species("Viburnum opulus", "Acer campestre", T)

# Presumably a typo while entering the data
beobachtungen <- replace_species("Verbena officinalis", "Veronica officinalis", F)

# Nachbestimmt durch Jürgen Dengler
beobachtungen <- replace_species("Luzula pilosa", "Luzula luzulina", T)
beobachtungen <- replace_species_on_plot("Festuca valesiaca aggr.", "Festuca ovina aggr.", 191, T)
beobachtungen <- replace_species_on_plot("Koeleria pyramidata", "Koeleria marcantha", 222, T)
beobachtungen <- replace_species_on_plot("Poa pratensis", "Poa alpina", 222, T)
beobachtungen <- replace_species_on_plot("Poa annua", "Poa trivialis", 222, T)
beobachtungen <- replace_species_on_plot("Avenella flexuosa", "Festuca rubra aggr.", 222, T)
beobachtungen <- replace_species_on_plot("Agrostis capillaris", "Anthoxanthum odoratum", 227, T)
beobachtungen <- replace_species_on_plot("Briza media", "Agrostis gigantea", 254, T)
beobachtungen <- replace_species_on_plot("Poa annua", "Poa alpina", 260, T)
beobachtungen <- replace_species_on_plot("Myosotis arvensis", "Myosotis cf. arvensis", 260, T)
beobachtungen <- replace_species_on_plot("Polygonum viviparum", "Plantago serpentina aggr.", 285, T)
beobachtungen <- replace_species_on_plot("Festuca pratensis", "Festuca rubra aggr.", 285, T)
beobachtungen <- replace_species_on_plot("Poa annua", "Poa alpina", 285, T)
beobachtungen <- replace_species_on_plot("Leontodon helveticus", "Leontodon hispidus", 285, T)
beobachtungen <- replace_species_on_plot("Carex spec.", "Carex cf. ferruginea", 286, T)
beobachtungen <- replace_species_on_plot("Brachypodium spec.", "Phleum hirsutum", 286, T)
beobachtungen <- replace_species_on_plot("Avenella flexuosa", "Festuca rubra aggr.", 286, T)
beobachtungen <- replace_species_on_plot("Viola canina subsp. montana", "Viola cf. riviniana", 314, T)
beobachtungen <- replace_species_on_plot("Festuca rubra", "Festuca ovina aggr.", 314, T)
beobachtungen <- replace_species_on_plot("Myosotis arvensis", "Myosotis cf. sylvatica", 325, T)
beobachtungen <- replace_species_on_plot("Dryopteris spec.", "Dryopteris carthusiana", 325, T)
beobachtungen <- replace_species_on_plot("Festuca valesiaca aggr.", "Festuca ovina aggr.", 326, T)
beobachtungen <- add_species_to_plot("Sesleria caerulea", 326)
beobachtungen <- replace_species_on_plot("Saponaria ocymoides", "Eudicot spec.", 357, T)
beobachtungen <- replace_species_on_plot("Festuca valesiaca", "Festuca ovina aggr.", 357, T)
beobachtungen <- replace_species_on_plot("Galium megalospermum", "Galium cf. tricornutum", 358, T)
beobachtungen <- replace_species_on_plot("Galium spec.", "Galium cf. tricornutum", 378, T)
beobachtungen <- replace_species_on_plot("Viola spec.", "Viola cf. riviniana", 378, T)
beobachtungen <- replace_species_on_plot("Festuca violacea aggr.", "Festuca ovina aggr.", 390, T)
beobachtungen <- replace_species_on_plot("Poaceae", "Poa nemoralis", 455, T)
beobachtungen <- replace_species_on_plot("Poa pratensis", "Poa pratensis aggr.", 487, T)
beobachtungen <- replace_species_on_plot("Viola reichenbachiana", "Viola cf. reichenbachiana", 542, T)
beobachtungen <- replace_species_on_plot("Ranunculus spec.", "Ranunculus tuberosus", 542, T)
beobachtungen <- replace_species_on_plot("Pimpinella saxifraga", "Pimpinella nigra", 553, T)
beobachtungen <- replace_species_on_plot("Festuca ovina aggr.", "Festuca heterophylla", 574, T)
beobachtungen <- replace_species_on_plot("Galium rubrum aggr.", "Galium cf. tricornutum", 574, T)
beobachtungen <- replace_species_on_plot("Ranunculus spec.", "Ranunculus cf. tuberosus", 574, T)
beobachtungen <- replace_species_on_plot("Viola reichenbachiana", "Viola cf. riviniana", 574, T)
beobachtungen <- replace_species_on_plot("Festuca rubra", "Festuca heterophylla", 586, T)
beobachtungen <- replace_species_on_plot("Arabis hirsuta", "Arabis ciliata", 607, T)
beobachtungen <- add_species_to_plot("Phyteuma cf. betonicifolium", 607)
beobachtungen <- add_species_to_plot("Verbascum thapsus", 607)
beobachtungen <- replace_species_on_plot("Galium spec.", "Galium verum", 637, T)
beobachtungen <- replace_species_on_plot("Hieracium murorum aggr.", "Hieracium pictum", 637, T)
beobachtungen <- replace_species_on_plot("Solanum dulcamara", "Gehölz unbekannt", 637, T)
beobachtungen <- replace_species_on_plot("Lonicera xylosteum", "df. Veronica chamaedrys", 639, T)
beobachtungen <- replace_species_on_plot("Galium rubrum", "Galium verum", 702, T)
beobachtungen <- replace_species_on_plot("Apiaceae", "Daucus carota", 702, T)
beobachtungen <- replace_species_on_plot("Cirsium arvense", "Carduus nutans", 702, T)
beobachtungen <- replace_species_on_plot("Carlina acaulis", "Carduus nutans", 702, T)
beobachtungen <- replace_species_on_plot("Pimpinella saxifraga", "Pimpinella nigra", 702, T)
beobachtungen <- replace_species_on_plot("Pimpinella saxifraga", "Pimpinella nigra", 712, T)
beobachtungen <- replace_species_on_plot("Pyrola spec.", "Orthilia secunda", 745, T)
beobachtungen <- replace_species_on_plot("Pimpinella saxifraga", "Pimpinella nigra", 745, T)
beobachtungen <- replace_species_on_plot("Briza media", "Phleum phleoides", 769, T)
beobachtungen <- replace_species_on_plot("Poa bulbosa", "Poa molinerii", 769, T) # Poa perconcinna...
# these two species should be joined for all species in the data set
beobachtungen <- replace_species_on_plot("Potentilla verna", "Potentilla pusilla", 769, T)
beobachtungen <- replace_species_on_plot("Cirsium vulgare", "Carduus nutans", 769, T)
beobachtungen <- replace_species_on_plot("Pimpinella saxifraga", "Pimpinella nigra", 769, T)
beobachtungen <- replace_species_on_plot("Pimpinella saxifraga", "Pimpinella nigra", 778, T)
beobachtungen <- replace_species_on_plot("Festuca valesiaca aggr.", "Stipa pennata aggr.", 802, T)
beobachtungen <- replace_species_on_plot("Elymus repens", "Elymus hispidus", 802, T)
beobachtungen <- replace_species_on_plot("Muscari comosum", "Muscari spec.", 802, T)

View(beobachtungen[startsWith(beobachtungen$taxon_orig, "Galium"),])
plot_numbers_of_species("Luzula pilosa")
species <- beobachtungen[beobachtungen$releve_id == global_id_to_releve_id(802),]
species$taxon_orig[startsWith(species$taxon_orig, "Mus")]


# this has been confirmed
beobachtungen <- replace_species_on_plot("Pulmonaria mollis", "Pulmonaria mollis", 315, T)

# TODO...

# Spit out all plots with plants which have some sort of a "cf." associated
plot_numbers_of_species(beobachtungen$taxon_orig[beobachtungen$determinavit_cf == "CF"])

# beobachtungen$taxon_orig <- str_replace_all(beobachtungen$taxon_orig, " cf\\. ", " ")
# beobachtungen$taxon_orig <- str_replace_all(beobachtungen$taxon_orig, "cf\\. ", "")

# Replace plant names which were definitively used differently on the fire patch
beobachtungen <- replace_species("Lotus corniculatus", "Lotus corniculatus aggr.", F)
beobachtungen <- replace_species("Thymus spec.", "Thymus serpyllum aggr.", T)
beobachtungen <- replace_species("Sorbus aria", "Sorbus aria aggr.", F)
beobachtungen <- replace_species("Salix appendiculata", "Salix appendiculata / caprea", F)
beobachtungen <- replace_species("Salix caprea", "Salix appendiculata / caprea", F)
beobachtungen <- replace_species("Papaver dubium subsp. dubium", "Papaver dubium", F)
beobachtungen <- replace_species("Erysimum rhaeticum", "Erysimum rhaeticum aggr.", F)
beobachtungen <- replace_species("Stipa eriocaulis", "Stipa pennata aggr.", F)
beobachtungen <- replace_species("Festuca rubra", "Festuca rubra aggr.", F)
beobachtungen <- replace_species("Ranunculus tuberosus", "Ranunculus tuberosus aggr.", F)
beobachtungen <- replace_species("Knautia dipsacifolia", "Knautia spec.", F)
beobachtungen <- replace_species("Knautia arvensis", "Knautia spec.", F)
beobachtungen <- replace_species("Scabiosa columbaria", "Scabiosa columbaria subsp. columbaria", F)
beobachtungen <- replace_species("Artemisia campestris aggr.", "Artemisia campestris", F)
beobachtungen <- replace_species("Galium anisophyllon", "Galium pumilum aggr.", T)
beobachtungen <- replace_species("Galium pumilum", "Galium pumilum aggr.", T)
beobachtungen <- replace_species("Arabis hirsuta", "Arabis hirsuta aggr.", F)
beobachtungen <- replace_species("Carlina vulgaris", "Carlina vulgaris aggr.", F)
beobachtungen <- replace_species("Crataegus monogyna", "Crataegus monogyna aggr.", F)
beobachtungen <- replace_species("Aconitum lycoctonum subsp. neapolitanum", "Aconitum lycoctonum", F)
beobachtungen <- replace_species("Dactylorhiza maculata", "Dactylorhiza maculata subsp. fuchsii", F)
beobachtungen <- replace_species("Leontodon hispidus subsp. hispidus", "Leontodon hispidus", F)
beobachtungen <- replace_species("Achillea millefolium", "Achillea millefolium aggr.", F)
beobachtungen <- replace_species("Epipactis helleborine", "Epipactis helleborine aggr.", F)
beobachtungen <- replace_species("Phleum pratense", "Phleum pratense aggr.", F)
beobachtungen <- replace_species("Arenaria serpyllifolia", "Arenaria serpyllifolia aggr.", F)
beobachtungen <- replace_species("Euphrasia rostkoviana", "Euphrasia rostkoviana subsp. rostkoviana", F)
beobachtungen <- replace_species("Ononis spinosa", "Ononis spinosa aggr.", F)
beobachtungen <- replace_species("Myosotis sylvatica", "Myosotis sylvatica aggr.", F)
beobachtungen <- replace_species("Pulmonaria mollis", "Pulmonaria australis", T)
beobachtungen <- replace_species("Poa pratensis", "Poa pratensis aggr.", T)
beobachtungen <- replace_species("Festuca laevigata", "Festuca ovina aggr.", F)
beobachtungen <- replace_species("Chaerophyllum hirsutum", "Chaerophyllum hirsutum aggr.", F)
beobachtungen <- replace_species("Luzula sylvatica", "Luzula sylvatica aggr.", F)
beobachtungen <- replace_species("Anthoxanthum odoratum", "Anthoxanthum odoratum aggr.", F)
beobachtungen <- replace_species("Ranunculus montanus", "Ranunculus montanus aggr.", F)
beobachtungen <- replace_species("Festuca violacea", "Festuca violacea aggr.", F)
beobachtungen <- replace_species("Hieracium pilosum", "Hieracium villosum aggr.", F)
beobachtungen <- replace_species("Galium rubrum", "Galium rubrum aggr.", F)
beobachtungen <- replace_species("Poa angustifolia", "Poa pratensis aggr.", T)
beobachtungen <- replace_species("Festuca valesiaca aggr.", "Festuca ovina aggr.", T)


# Uncertain whether these renaimings are correct...
# beobachtungen <- replace_species("Petrorhagia saxifraga", "Petrorhagia prolifera", F)
beobachtungen <- replace_species("cf. Epipactis atrorubens", "Epipactis spec.", F)
beobachtungen <- replace_species("cf. Epipactis helleborine", "Epipactis spec.", F)
beobachtungen <- replace_species("Pyrola minor", "Pyrola spec.", F)
beobachtungen <- replace_species("Pyrola media", "Pyrola spec.", F)


length(unique(beobachtungen$taxon_orig))

main <- read_csv("../Daten/Leuk/Erste Daten von Tom/data_2004_2023_main.csv")
mosses <- read_csv("../Daten/Leuk/Hand Curated/moss_taxa.csv")
main <- main[!(main$`Species_unified_2004-23` %in% mosses$moss_taxa),]
length(unique(main$`Species_unified_2004-23`))

complete_list <- unique(append(main$`Species_unified_2004-23`, beobachtungen$taxon_orig))
length(complete_list)

all_taxa <- data.frame(taxon = complete_list)
all_taxa$'On Fire Patch' <- complete_list %in% main$`Species_unified_2004-23`
all_taxa$'Beside Fire Patch' <- complete_list %in% beobachtungen$taxon_orig


# All species which are believed to be only on the surrounding plots and not on the fire patch.
verified_as_plausible <- c(
  "Asplenium adiantum-nigrum",
  "Hypochaeris maculata",
  "Hieracium glaucinum aggr.",
  "Muscari comosum",
  "Calamagrostis spec.",
  "Medicago falcata",
  "Angelica sylvestris",
  "Paris quadrifolia",
  "Galium rotundifolium",
  "Centaurea valesiaca",
  "Asteraceae",
  "Ajuga reptans",
  "Viola canina subsp. montana",
  "Silene dioica",
  "Viola odorata",
  "Orobanche minor",
  "Astrantia major",
  "Aegopodium podagraria",
  "Poa bulbosa",
  "Luzula nivea",
  "Sorbus chamaemespilus",
  "Pinus mugo",
  "Koeleria pyramidata",
  "Goodyera repens",
  "Adenostyles alliariae",
  "Cerastium fontanum",
  "Cerastium arvense",
  "Ononis repens",
  "Amelanchier humilis", # Neophyte
  "Moneses uniflora",
  "Campanula rhomboidalis",
  "Stachys byzantina",
  "Luzula spicata",
  "Phleum hirsutum",
  "Vicia sativa",
  "Petrorhagia saxifraga",
  "Leontodon crispus" #suspicious but bag with proofs cannot be found
)

# Compute the average species richness
mean((beobachtungen |> group_by(releve_id) |> summarise(n = length(unique(taxon_orig))))$n)
```

Clean up the remarks column and add a1 and a10 column
```{r}
beobachtungen$rem[beobachtungen$rem == "A19"] <- "A10"
beobachtungen$rem[beobachtungen$rem == "S10"] <- "A10"
beobachtungen$rem[beobachtungen$rem == "Drüsig behaart"] <- NA

beobachtungen$a1 <- 0 + (beobachtungen$rem == "A1")
beobachtungen$a1[is.na(beobachtungen$a1)] <- 0
beobachtungen$a10 <- (beobachtungen$rem == "A10" | beobachtungen$rem == "A1")
beobachtungen$a10[is.na(beobachtungen$a10)] <- 0
beobachtungen$b1 <- NA
beobachtungen$b10 <- NA
beobachtungen$c1 <- NA
beobachtungen$c10 <- NA
beobachtungen$d1 <- NA
beobachtungen$d10 <- NA
```

Join with header data
```{r}
x_min <- 2614000.0000
x_max <- 2618000.0000
y_min <- 1129000.0000
y_max <- 1133000.0000

header <- read_delim("../Daten/Leuk/Climax Daten 2024/Orig_Header-Vegetations-Aufnahmen.csv")
header <- header[c("id", "name", "trees_height", "trees_cover", "bushes_height", "bushes_cover", "herbaceous_height", "herbaceous_cover", "moss_cover")]
names(header)[2] <- "global_id"

all_data <- full_join(beobachtungen, header, join_by(releve_id == id))
```

Add x and y coordinates:
```{r}
all_data$coordX <- (all_data$global_id - 1) %% 33 * 125 + x_min - 2000000
all_data$coordY <- y_max - 1000000 - floor((all_data$global_id - 1) / 33) * 125
```

Add altitude, aspect and slope:
```{r}
raster <- read_delim("../Daten/Intermediate/slope_and_aspect.csv")
all_data <- inner_join(all_data, raster, join_by(global_id == global_id))
```


```{r}
names(all_data)
all_data$plot_no <- NA
all_data$year <- "climax"
all_data <- all_data[c("global_id", "plot_no", "year", "coordX", "coordY", "altitude", "taxon_orig", "supplements.releve_stratum", "supplements.cover_abs", "a1", "a10", "b1", "b10", "c1", "c10", "d1", "d10")]
```

Add Bodentiefe to the data
```{r}
bodentiefen <- read_delim("../Daten/Leuk/Climax Daten 2024/climax_bodentiefen.csv")
means <- rowMeans(bodentiefen[-1])
medians <- apply(bodentiefen[-1], 1, median)
bodentiefen <- data.frame(plotid = bodentiefen$PlotID, bodentiefemittel04 = means, bodentiefemedian04 = medians)

all_data <- full_join(all_data, bodentiefen, join_by(global_id == plotid))
```

Adjust column naming and remove columns to match combined data
```{r}
names(all_data)
names(all_data)[names(all_data) == "altitude"] = c("elevation_m")
names(all_data)[names(all_data) == "supplements.releve_stratum"] = c("layer")
names(all_data)[names(all_data) == "supplements.cover_abs"] = c("percentage200")
names(all_data)[names(all_data) == "taxon_orig"] = c("Species_unified_2004-23")
all_data$distancewald_korr <- NA
all_data$aschemittel04 <- NA
all_data$aschemedian04 <- NA
all_data <- all_data[,c("global_id", "plot_no", "year", "coordX", "coordY", "elevation_m", "Species_unified_2004-23", "layer", "percentage200", "a1", "a10", "b1", "b10", "c1", "c10", "d1", "d10", "distancewald_korr", "aschemittel04", "aschemedian04", "bodentiefemittel04", "bodentiefemedian04")]
```

Clean up the layers
```{r}
all_data$layer[all_data$layer == "ψ"] <- "♃" # Fix Moosschicht to Krautschicht for a single Achillea millefolium aggr.

all_data$layer[all_data$layer == "Y"] <- 1 # Baumschicht
all_data$layer[all_data$layer == "v"] <- 2 # Strauchschicht
all_data$layer[all_data$layer == "♃"] <- 3 # Krautschicht

all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Juniperus communis"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Adenostyles alliariae"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Poa alpina"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Paris quadrifolia"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Muscari cf. comosum"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Pimpinella cf. nigra"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Arabis hirsuta aggr."] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Cotoneaster cf. tomentosus"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Ononis pusilla"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Carex montana"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Pflanze"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Brachypodium cf. rupestre"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Hieracium cf. pilosella"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Polypodium vulgare"] <- 3
all_data$layer[is.na(all_data$layer) & all_data$`Species_unified_2004-23` == "Thymus serpyllum aggr."] <- 3

unique(all_data$`Species_unified_2004-23`[is.na(all_data$layer)])
```

Write data to file:
```{r}
write_csv(all_data, "../Daten/Intermediate/cleaned_climax_data.csv")
```
